---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753AMARA2024)
```

# First Function: In class

We created a function to calculate the square of a vector of numbers in class. This was the first function added to the package.

In the next example, we are squaring each element of the vector [1:10] = [ 1 2 3 4 5 6 7 8 9 10 ]

```{r}
mysquare(1:10)
```

# Lab 5 Function: Binomial experiment simulation

The mybin(iter, n, p) function simulates a binomial experiment and visualizes the results. It iterates over iter # of experiments where n trails are generated in each experiment, and the number of successes per experiment are stored. A table of the number of successes across all experiements is outputted along with a barplot showing the proportions of each possible number of successes (from 0 to n). 

```{r}
mybin()
```


# Lab 6: Normal Distribution Probability

The myncurve(mu, sigma, a) function displays the curve, shaded area between the curve and x axis from -∞ to x=a, and calculates the area (i.e. probability P(X \<= a)), which is released to the command-line in a list along with the mean (mu) and standard deviation (sigma). This is all for a normal distribution.

In this example, the function is Y \~ N(10, 5), P(X \<= 6)

```{r}
myncurve(mu=10, sigma=5, a=6)
```

# Piecewise Linear Regression

The myf function computes the value of a piecewise linear regression at a given value of x given you provide the x to evaluate at, the knot point xk, and a vector of coefficients (first is intercept, second is slope for x, third is slope adjustment for values of x greater than xk). It outputs the value of the piecewise regression.

```{r}
myf(0, 18, coef=c(6.2188237,0.6741809,-0.5803229))
```

# Lab 8 Central Limit Theorem for Binomial Distribution

The function mycltb demonstrates the Central Limit Theorem for the binomial distribution. It generates iter samples of size n from a binomial distribution using rbinom function, calcualtes the mean of each sample for each iteration, and creates a histogram of the sample means.It compares the histogram to the expected normal distribution from the CLT, which approximates the distribution of the sample means as a normal distribution with mean $n*p$ and standard deviation $\sqrt{n*p*(1-p)}$.

```{r}
mycltb(n=10,iter=10000,p=0.3)
```

# Lab 9 Bootstrap Confidence Interval Histogram

The function myboot2 performs a bootstrap analysis to create a histogram of the bootstrap sample statistics and calculate a confidence interval. The function generates iter bootstrap samples by resampling the data x with replacement.
For each bootstrap sample, it calculates the statistic (mean by default) using the specified function fun.
It then calculates the confidence interval (CI) using the quantile function, which returns the values corresponding to the lower and upper percentiles defined by alpha.
The function returns a histogram of the bootstrap sample statistics, with the point estimate and confidence interval marked.
It also returns a list containing the confidence interval, function used, original data, bootstrap sample statistics, and point estimate.

```{r}
myboot2(x=c(1,1,1,2,2,2,2,3,3,4,4,4))
```

# Project 1 Overbooking Problem to find Optimal Tickets Sold


The function ntickets solves the overbooking problem by finding the optimal number of tickets to sell for a flight to minimize the probability of overbooking, using both discrete (binomial) and continuous (normal) models. 

The function fd(n) calculates the probability of overbooking for different values of n (number of tickets sold). It finds the smallest n where the probability of overbooking is less than or equal to gamma.

The function fc(x) uses a normal distribution approximation to find the optimal n that minimizes overbooking risk, using the mean and standard deviation of the number of show-ups.

The function prints a list with the optimal number of tickets for both the discrete (nd) and continuous (nc) models, along with the input parameters.

Two plots are created:
A plot showing the discrete objective function (overbooking probability) versus the number of tickets sold (n).
A plot for the continuous model, using the normal approximation, showing the same objective.


# Lab 11 Confidence Interval for mu given single sample x

The function myci calculates the 95% confidence interval for the mean (mu) of a population based on a single sample x. The function calculates the sample size n and the t-distribution critical value t for a 95% confidence level using the qt function. It then computes the ci using $CI=(\bar{x}-t\frac{sd(x)}{\sqrt(n)},\bar{x}+t\frac{sd(x)}{\sqrt(n)})$

```{r}
myci(x = rnorm(30,mean=10,sd=12))
```

