---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753AMARA2024)
```

# First Function: In class

We created a function to calculate the square of a vector of numbers in class. This was the first function added to the package.

In the next example, we are squaring each element of the vector [1:10] = [ 1 2 3 4 5 6 7 8 9 10 ]

```{r}
mysquare(1:10)
```

# NEED TO UPDATE FOR FUNCTIONS myf, mybin

# Lab 6: Normal Distribution Probability

The myncurve(mu, sigma, a) function displays the curve, shaded area between the curve and x axis from -∞ to x=a, and calculates the area (i.e. probability P(X \<= a)), which is released to the command-line in a list along with the mean (mu) and standard deviation (sigma). This is all for a normal distribution.

In this example, the function is Y \~ N(10, 5), P(X \<= 6)

```{r}
myncurve(mu=10, sigma=5, a=6)
```
